  \begin{thebibliography}{9}

	  \bibitem{AmpRobertson}
		  I.D. Robertson, \emph{RFIC and MMIC Design and Technology}.
		  The Institution of Engineering and Technology,
		  2nd edition,
		  2001

	  \bibitem{Pozar}
i		  David M. Pozar, \emph{Microwave and RF Design of Wireless Systems}.
		  John Wiley \& Sons,
		  1st edition,
		  2001

	  \bibitem{CreeDS}
		  \emph{Cree CGH40010 Datasheet}.
		  Cree, Inc. 
		  Rev 3.2,
		  April 2012

	  \bibitem{5WLTE}
		  K. Niotaki, A. Collado, A. Georgiadis, J. Vardakas, \emph{5 Watt GaN HEMT Power Amplifier for LTE}.
		  Centre Tecnologic de Telecomunicacions de Catalunya.
		  Research paper published in Radioengineering, Vol. 23, No. 1, April 2014. Available for download from \url{http://www.radioeng.cz/fulltexts/2014/14_01_0338_0344.pdf} (visited on November 19, 2014)

	  \bibitem{EE481}
		  Keith W. Whites, \emph{Amplifier Stability}, Lecture notes from the course EE481 Microwave Engineering at South Dakota School of Mines and Technology.
		  Available for download from \url{http://whites.sdsmt.edu/classes/ee481/notes/481Lecture34.pdf} (visited on November 19, 2014)

	  \bibitem{MW101}
		  \emph{Stability Factor}, article at microwawes101.com. \url{http://www.microwaves101.com/encyclopedias/stability-factor} (visited on November 19, 2014)

	  \bibitem{DHALL}
		  David Hall, \emph{Understanding Intermodulation Distortion Measurements}. \url{http://electronicdesign.com/communications/understanding-intermodulation-distortion-measurements} (visited on November 19, 2014)

  \end{thebibliography}

  \section{Figures from external sources}
  Below is a list of the sources for all figures we did not make ourselves. All sources were visited on November 19, 2014.
  \begin{itemize}
	  \item{Figure~\ref{fig:fig_Load_line}: \url{http://www.electronics-tutorials.ws/amplifier/amp16.gif}}
	  \item{Figure~\ref{fig:fig_sparam_vis}: \href{http://upload.wikimedia.org/wikipedia/en/thumb/5/5c/TwoPortNetworkScatteringAmplitudes.svg/540px-TwoPortNetworkScatteringAmplitudes.svg.png}{\texttt{http://upload.wikimedia.org/wikipedia/en/thumb/5/5c/ \\ TwoPortNetworkScatteringAmplitudes.svg/ \\ 540px-TwoPortNetworkScatteringAmplitudes.svg.png}}}
	  \item{Figure~\ref{fig:fig_reflection_ex}: \url{http://whites.sdsmt.edu/classes/ee481/notes/481Lecture34.pdf}, page 2}
	  \item{Figure~\ref{fig:fig_distortion_vis}: \url{http://electronicdesign.com/site-files/electronicdesign.com/files/uploads/2013/10/1107_MakingWaves_F1.gif}}
  \end{itemize}
